Query Optimization for Dynamic Imputation

### 2017-07-10 paper/introduction.tex
Rephrase results

% Implications
Our approach enables an exploratory analysis workflow in which the analyst can issue
standard SQL queries over a data set, even if that data has missing values.
These queries execute between \lowxalphazero{} and \highxalphazero{} times faster than
imputing all missing values and then running queries (the traditional approach). Furthermore, the results obtained with this approach
are similar in quality to those obtained with the traditional imputation approach
--- between \lowsmapealphazero{} and \highsmapealphaone{}
percent --- in our empirical results over real-world data sets (see~\Cref{sec:experiments}
for details).

>>>>

% Implications
Our approach enables an exploratory analysis workflow in which the analyst can issue
standard SQL queries over a data set, even if that data has missing values.
These queries execute between \lowxalphazero{} and \highxalphazero{} times faster than
imputing all missing values and then running queries (the traditional approach). Furthermore, the results obtained with this approach
are similar in quality to those obtained with the traditional imputation approach
--- between \lowsmapealphazero{} and \highsmapealphazero{}
percent --- in our empirical results over real-world data sets (see~\Cref{sec:experiments}
for details).

### 2017-07-10 paper/main.tex
Rephrase results

\begin{abstract}
  Missing values are common in data analysis and present a usability challenge.
  Users are forced to pick between removing tuples with missing values or creating a cleaned version of their data by applying a relatively expensive imputation strategy.
  Our system, \ProjectName{}, incorporates imputation into a cost-based query optimizer, performing necessary imputations on-the-fly for each query.
  This allows users to immediately explore their data, while the system picks the optimal placement of imputation operations.
  % This placement is based on the specific query issued and a user-provided parameter that trades off data quality and runtime performance.
  % We incorporate the imputation operators into the relational algebra, allowing for traditional optimizations to take place.
  We evaluate this approach on three real-world survey-based datasets.
  % from the \textit{Center for Disease Control and Prevention} and \textit{freeCodeCamp}.
  Our experiments show that our query plans execute between \lowxalphazero{} and \highxalphazero{} times faster than first imputing the base tables.
  Furthermore, we show that the query results from on-the-fly imputation differ from the
  traditional base-table imputation approach by \lowsmapealphazero{}--\highsmapealphaone{}\%.
  Finally, we show that while dropping tuples with missing values that fail query constraints discards \lowcountfractionlostalphaone--\highcountfractionlostalphaone\% of the data, on-the-fly imputation loses only \lowcountfractionlostalphazero--\highcountfractionlostalphazero\%.
\end{abstract}

>>>>

\begin{abstract}
  Missing values are common in data analysis and present a usability challenge.
  Users are forced to pick between removing tuples with missing values or creating a cleaned version of their data by applying a relatively expensive imputation strategy.
  Our system, \ProjectName{}, incorporates imputation into a cost-based query optimizer, performing necessary imputations on-the-fly for each query.
  This allows users to immediately explore their data, while the system picks the optimal placement of imputation operations.
  % This placement is based on the specific query issued and a user-provided parameter that trades off data quality and runtime performance.
  % We incorporate the imputation operators into the relational algebra, allowing for traditional optimizations to take place.
  We evaluate this approach on three real-world survey-based datasets.
  % from the \textit{Center for Disease Control and Prevention} and \textit{freeCodeCamp}.
  Our experiments show that our query plans execute between \lowxalphazero{} and \highxalphazero{} times faster than first imputing the base tables.
  Furthermore, we show that the query results from on-the-fly imputation differ from the
  traditional base-table imputation approach by \lowsmapealphazero{}--\highsmapealphazero{}\%.
  Finally, we show that while dropping tuples with missing values that fail query constraints discards \lowcountfractionlostalphaone--\highcountfractionlostalphaone\% of the data, on-the-fly imputation loses only \lowcountfractionlostalphazero--\highcountfractionlostalphazero\%.
\end{abstract}
